---
title: "The Amazing Presentation: Go Lean"
author: "Benjamin Jacobson"
date: "October 5, 2016"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Lean Methodology

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## The Lean Methodology

- Build
- Measure
- Learn


## Creating an MVP

### Why an MVP
1. The goal of creating an MVP is to make the minimal amount of effort, while being to test the hypothesis in question.
2. Upon builing and measuring customer behavior, learning is the goal.
3. Validated learning results when the changes from the experiment yields a, hopefully, actionable insght based on the hypothesis. 

### If you build it, they may not come
- MVP allows you to test hypothesis of whether a sustainable business can be created.
- Minimal waste is created (i.e. time, resources)

## Summary of Car Data
```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

## Slide with Leaflet

```{r, echo=F}
library(leaflet)
my_map <- leaflet() %>%  addTiles()
my_map
```
